Symbolic Weighted Language Models and\\ Quantitative Parsing over Infinite Alphabets

### 2021-07-10 main.tex
Gain de place (1)

\begin{example}

Consider once more the scores of Example~\ref{ex:running}.
$\Deltai$ represents the set of music events of the form $<\nu, \tau>$
where $\nu$ is either a note (e.g. A4), the continuation symbol $-$, or a
rest symbol R. $\Deltac$ and  $\Deltar$ are used to encode the score structure:
Let $\Deltac = \{\langle, \prec\}$ and  $\Deltar = \{\rangle, \succ\}$ where $\langle$
(resp. $\rangle$)
and $\prec$ (resp. $\succ$) correspond to start/end of measures, and start/end of
tuplets. Then  \includegraphics[scale=0.20]{pictures/score5.png}
is encoded with the nested word $\langle \prec 0, \frac{3}{4}, \frac{7}{8} \succ \rangle \langle \prec 1, \frac{4}{3}, \frac{5}{3}  \succ \rangle$
\endex
\end{example}

@@

\noindent
The infinite sums in the updates of $d$ in Algorithm~\ref{algo:Dijkstra},
Figure~\ref{fig:best-update}
are well defined
since~$\Semiring$ is complete.

@@

  \item The \SWT $T$ evaluates a ``fitness measure''  that expresses
    a correspondance between a performance and its notation. See Example~\ref{ex:SWT}.
\item The \SWVPA $A$ expresses a cost related to the music notation. One possibility
 is to relate this cost to the structural complexity: given a set of equivalent
 representations, we aim at choosing the simpler one. For instance
 \includegraphics[scale=0.20]{pictures/score4.png} should be favored
 on \includegraphics[scale=0.20]{pictures/score5.png}, although both yield
 a same linearization. Costs  can be expressed
 in the grammar with weight associated to each production rule. See Example~\ref{rules-division}.

 \end{enumerate}
Therefore, the framework, applied to the transcription problem, allows to find an optimal
solution that considers both the fitness of the result, and its structural complexity.
\end{example}

\begin{example}\label{rules-division}
The recursive subdivision of time that leads to hierarchichal
structures of music notation can be modeled as
production rules. Since there exists several possible division,
rules can be weighted in the tropical semiring.
For instance, the following production rules define two possible divisions
of a time interval into respectively a duplet and a triplet.
\[
\rho_1: q_0 \xrightarrow{0.06} \< q_{1}, q_{2}>,\
\rho_2: q_0 \xrightarrow{0.12} \< q_{1}, q_{2}, q_{2}>.
\]
Further binary divisions of time sub-intervals %represented respectively by~$q_2$ and~$q_3$
are possible with:
\[
\rho_3:\,q_2 \xrightarrow{0.1} \< q_{3}, q_{3}>, \
\rho_4:\,q_3 \xrightarrow{0.11} \< q_{4}, q_{4}>. \
\]

The latter shows a subdivision
based on the rules from Example~\ref{rules-division}. The first measure ($I_1$)
results from the successive applications of  rules $\rho_1$ (division in two)
and rules $\rho_3$ (division of the second half) in two. The second measure
is a division in three obtained by rule $\rho_3$. It follows that the notation
defines the sequence of timestamps $0, \frac{3}{4}, \frac{7}{8}, 1, \frac{4}{3}, \frac{5}{3}$.
\end{example}

>>>>

\begin{example}\label{ex:nested-word}
Consider once more the scores of Example~\ref{ex:running}.
$\Deltai$ represents the set of music events of the form $<\nu, \tau>$
where $\nu$ is either a note (e.g. A4), the continuation symbol $-$, or a
rest symbol R. $\Deltac$ and  $\Deltar$ are used to encode the score structure:
Let $\Deltac = \{\langle, \prec\}$ and  $\Deltar = \{\rangle, \succ\}$ where $\langle$
(resp. $\rangle$)
and $\prec$ (resp. $\succ$) correspond to start/end of measures, and start/end of
tuplets. Then  \includegraphics[scale=0.20]{pictures/score5.png}
is encoded with the nested word $\langle \prec 0, \frac{3}{4}, \frac{7}{8} \succ \rangle \langle \prec 1, \frac{4}{3}, \frac{5}{3}  \succ \rangle$
\endex
\end{example}

@@

The infinite sums in the updates of $d$ in Algorithm~\ref{algo:Dijkstra},
Figure~\ref{fig:best-update}
are well defined
since~$\Semiring$ is complete.

@@

  \item The \SWT $T$ evaluates a ``fitness measure''  that expresses
    a correspondance between a performance and its notation. See Example~\ref{ex:SWT}.
\item The \SWVPA $A$ expresses a cost related to the music notation. One possibility
 is to relate this cost to the structural complexity: given a set of equivalent
 representations, we aim at choosing the simpler one. For instance
 \includegraphics[scale=0.20]{pictures/score5.png} should be favored
 on \includegraphics[scale=0.20]{pictures/score4.png}. Costs  can be expressed
 in the grammar as weights associated to each production rule.
 For instance, the following production rules define two possible divisions
 of a time interval into respectively a duplet and a triplet. Each comes with
 a specific cost.
 \[
 \rho_1: q_0 \xrightarrow{0.06} \< q_{1}, q_{2}>,\
 \rho_2: q_0 \xrightarrow{0.12} \< q_{1}, q_{2}, q_{2}>.
 \]
 Further binary divisions of time sub-intervals %represented respectively by~$q_2$ and~$q_3$
 are possible with:
 \[
 \rho_3:\,q_2 \xrightarrow{0.1} \< q_{3}, q_{3}>, \
 \rho_4:\,q_3 \xrightarrow{0.11} \< q_{4}, q_{4}>. \
 \]

Score \includegraphics[scale=0.20]{pictures/score5.png} is obtained as follows:
the first measure
 results from the successive applications of  rules $\rho_1$ (division in two)
 and rules $\rho_3$ (division of the second half) in two. The second measure
 is a division in three obtained by rule $\rho_3$. One obtains a parse tree
 that can be linearized in the nested word of Example~\ref{ex:nested-word}.
 \end{enumerate}
Therefore, the framework, applied to the transcription problem, allows to find an optimal
solution that considers both the fitness of the result, and its structural complexity.
\end{example}
